Data Specialization for a Staged Lambda Calculus

### 2015-02-14 paper/figures/splitting-overview.tex
changed name of pipes

\textbf{Single-Output Pipelines:}

@@

	\hspace{4em} $\pipeS p l r$ is the single-output pipeline to be evaluated

@@

\textbf{Mutiple-Output Pipelines:}

@@

	\hspace{4em} $\pipeM c l r$ is the multi-output pipeline to be evaluated

@@

\begin{minipage}[t]{0.45\textwidth}
Splitting Terms: $(\colmix e A) \splitonesym \pipeM p l r$, where
\par \hspace{2em} $\colmix e A$ is the \lang\ input term to be split 
\par \hspace{2em} $\pipeM p l r$ is the resulting multi-output pipeline
\\
Masking Partial Values: $[\xi;v] \vsplito \mval i q$, where
\par \hspace{2em} $[\xi;v]$ is a partial value in \lang, resulting from $\redonesym$
\par \hspace{2em} $\mval i q$ is the resulting masked value
\end{minipage}
&

\begin{minipage}[t]{0.45\textwidth}
Splitting Terms: $(\coltwo e A) \splittwosym \pipeS p l r$, where 	
\par \hspace{2em} $\coltwo e A$ is the \lang\ input term to be split
\par \hspace{2em} $\pipeS p l r$ is the resulting single-output pipeline
\end{minipage}

>>>>

\textbf{Syntactically Seperated Term with Stage \bbtwo\ Output:}

@@

	\hspace{4em} $\pipeS p l r$ is the syntactically seperated term to be evaluated

@@

\textbf{Syntactically Seperated Term with Multistage Output:}

@@

	\hspace{4em} $\pipeM c l r$ is the syntactically seperated term to be evaluated

@@

\begin{minipage}[t]{0.45\textwidth}
Splitting Terms: $(\colmix e A) \splitonesym \pipeM p l r$, where
\par \hspace{2em} $\colmix e A$ is the \lang\ input term to be split 
\par \hspace{2em} $\pipeM p l r$ is the syntactically seperated result
\\
Masking Partial Values: $[\xi;v] \vsplito \mval i q$, where
\par \hspace{2em} $[\xi;v]$ is a partial value in \lang, resulting from $\redonesym$
\par \hspace{2em} $\mval i q$ is the resulting masked value
\end{minipage}
&

\begin{minipage}[t]{0.45\textwidth}
Splitting Terms: $(\coltwo e A) \splittwosym \pipeS p l r$, where 	
\par \hspace{2em} $\coltwo e A$ is the \lang\ input term to be split
\par \hspace{2em} $\pipeS p l r$ is the syntactically seperated result
\end{minipage}

### 2015-02-14 paper/splitting.tex
changed name of pipes

Similar to above, we also define a $\sepredtwosym$ relation which can be used to evaluate \texttt{pipeM} terms,
with one complication arising from the fact that \lang\ terms at world \bbonem\ produces multistage output.
For example, consider the term
\begin{lstlisting}
(next {1+2}, pure{3+4})
\end{lstlisting}
which reduces (via $\redonesym$) to the residual table and partial value
\begin{lstlisting}
[yhat |-> 1+2] (next {yhat}, pure{7})
\end{lstlisting}
Since this output has interleaved stages, so theres no way a syntactically seperated term could directly reduce to it.

>>>>

Similar to above, we also define a $\sepredtwosym$ relation which can be used to evaluate \texttt{sepM} terms,
with one complication arising from the fact that \lang\ terms at world \bbonem\ produces multistage output.
For example, consider the term
\begin{lstlisting}
(next {1+2}, pure{3+4})
\end{lstlisting}
which reduces (via $\redonesym$) to the residual table and partial value
\begin{lstlisting}
[yhat |-> 1+2] (next {yhat}, pure{7})
\end{lstlisting}
Since this output has interleaved stages, so theres no way a syntactically seperated term could directly reduce to it.
